Do return series have power-law tails with the same index?

### 2017-06-05 papers/FX/draft.tex
Some revision to the importance sampling paper. Made C++ programs for Johannes' paper.

\subsection{A utility based argument for equal tail-indices}\label{sec:3}
In this section we give an argument based on economic theory that
suggests equality of  tail-indices for equity return series.
We follow an approach by Routledge and Zin
\cite{routledge2010generalized} who introduced the notion of
Generalized Disappointment Aversion (GDA). We consider the risky
payoff $C$ of an investor and assume that it has a continuous \ds\ on
$(0,\infty)$ with \df\ $F_C$. Let $u$ be a utility \fct\ assumed to be
increasing and concave on $(0,\infty)$.  Following Routledge and Zin
\cite{routledge2010generalized},
the utility of an agent with GDA preferences is given by
\beao% \label{eq:xxie0}
  \wt u&=& \E [u(C)] - b\, \int_{0}^{\delta v}
  \big[ u(\delta \,v) - u(x) \big] F_C(dx)\,,
  %&=&
  %\E u(C) - b \E\big[\big(u(\delta \,v) - u(C)\big)\1( C \le  \delta \,v)\big]\,,
\eeao
where $\delta $ and $v$ are positive constants, and $b\ge 0$.
  Here $v$ can be thought of as the {\em certainty payoff} equivalent to the
 risky payoff $C$; $\delta$ tunes the {\em threshold of 
   disappointment} in proportion to $v$; $b$ determines the extra
 weight given to the expected return of $C$ when $C$ is below the
 disappointment threshold $\delta v$.
 If $b=0$, preferences are the classical expected utility. If
 $\delta=1$ and $b>0$ preferences follow Gul's \cite{gul:1991} 
disappointment aversion which were generalized by Routledge and Zin
\cite{routledge2010generalized}.
\par
An agent guided by the utility function $u$ will seek to maximize the
\fct al $\wt u$.
Routledge and Zin assumed a power-law utility function 
%\beam\label{eq:u}
%u(x)=\frac{1}{1 - \gamma}\,x^{1 - \gamma}\,,\quad \gamma>0\,. 
%\eeam
% In practice it is more often to observe $\gamma > 1$ {\blue Let's
% consult Casper for references.}
%We focus on the case $\gamma > 1$ and hence adopt a more convenient
%notation:
\beam\label{eq:hjyr}
u(x)=-\frac{1}{\xi}\,x^{-\xi}\,,\quad \xi>0\,. 
\eeam

%In practice it is more often to observe $\gamma > 1$ {\blue Let's
%consult Casper for references.} Therefore we adopt a more convenient
For the sake of argument, we assume that an investor initially has one
unit of wealth. He invests $1-\phi\in (0,1)$ units in a risk-free 
bond with interest rate $r>0$ and $\phi$ units in a risky asset with
return $X$ over one time unit, i.e.,
\beam\label{eq:xxie1}
  C(X) = (1 - \phi)\, \ex^{r} + \phi \,\ex^{X}\,.
\eeam
Then we have 
\beao
\wt u(F_X, \phi) &=& \E [u(C)] + b\, \E \big[u(C)\1(C \le  \delta v)\big] - b \,u(\delta\, v) F_X(q)\,,
\eeao
where $F_X$ is the \df\ of $X$  and
\beao
  q = %q(r, \phi) &:=& \log \left( {
      %\delta v - (1 - \phi) e^r
      %\over
      %\phi
    % \right) 
\log\Big(
    \ex^r + {\delta \,v - \ex^r \over \phi}
  \Big)\,.
\eeao
Note that $C \le \delta v$ \fif\ $X \le  q$. 
\par
Naturally, if an agent invests in
a risky asset instead of a riskless bond, he expects to obtain a
higher (on average) return from the risky asset than he is guaranteed from the
riskless bond. In our notation, this means $\delta \,v > \ex^r$ or
$q > r $. For given $b,\delta,v$, the \fct al $\wt u$  depends only on $\phi$ and $F_X$,
$\wt u=\wt u (F_X, \phi)$.
We assume that
\beao
\wt u_{\rm max}=\wt u_{\rm max}(F_X) = \max_{0 \le  \phi \leq 1} \wt u (F_X,\phi)
\eeao
exists and that the maximum is achieved at a unique $\hat\phi \in (0, 1)$.

@@

\begin{minipage}{0.5\linewidth}
  \includegraphics[width=\textwidth]{power_utilities.png}
\end{minipage}\hfill
\begin{minipage}{0.42\textwidth}
  In this graph we show two power-utility functions $u$. We see that
  $u(x)$ grows slower and saturates later for small $\xi$ than for
  large $\xi$. The latter case represents an agent who is more
  tolerant about low consumption and seeks wealth more
  aggressively. In other words, he is less risk-averse than one with a
  larger $\xi$. Such an agent will therefore invest more heavily in
  equity, as shown in Figure~\ref{fig:phi_hat_pareto}. Note that,
  while $\hat \phi$ changes nearly in the same in both graphs, the
  scales in the graphcs are very different.

\end{minipage}
{\red Needed? The following graph (figure \ref{fig:preference_pareto}) shows how
$\tilde u(\alpha, K, \wt\phi)$ changes with $\alpha$ and $K$.}
\begin{figure}[htb!]
  \begin{minipage}{0.25\linewidth}
    \includegraphics[width=\textwidth]{preference_pareto5e-1_A.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.25\linewidth}
    \includegraphics[width=\textwidth]{preference_pareto4_A.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.25\linewidth}
    \includegraphics[width=\textwidth]{preference_pareto5e-1.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.25\linewidth}
    \includegraphics[width=\textwidth]{preference_pareto4.pdf}
  \end{minipage}
  \caption{
   {\em The 1st and 2nd} graphs show
   $\tilde u_{\rm max}(\alpha, K)$, as a \fct\ of $\alpha$ and $K$
   in the two-sided Pareto model \eqref{eq:pareto} with $K'=0.012$,
   $\beta = 1.4$.
   Clearly, $\tilde u_{\rm max}(\alpha, K)$ increases with $\alpha$
   and decreases with $K$ when $K'$ and $\beta$ are fixed.
   {\em The 3rd and 4th} graphs show
   $\tilde u_{\rm max}(\alpha, K)$ as a \fct\ of $\alpha$
   and $K$ with $\beta = \alpha$ and $K' = K$.
   We choose the utility \fct\ $u$ from \eqref{eq:hjyr} for $\xi = 1/2$
   and $\xi = 4$. $b = 0.01$ in all cases.
  }
  \label{fig:preference_pareto}
\end{figure}

If the parameter $b$ is very small the GDA preference is closely
approximated by the mean-utility preference, corresponding to $b = 0$. 
In this case, we show in the proof of Lemma \ref{lemma:III} that the function
$U_{\text{all}}(x)$ may increase or decrease depending on particular conditions
on the values of $\xi$ and $(1 - \phi) e^r / \phi$. {\red Conditions?} Moreover, it
is also easily checked that, when $x \in (0, K(e^{1/\alpha} - 1)]$,
the {\red density?} function in the integral of \eqref{eq:ipf} increases
with $\alpha$; when $x \in (K(e^{1/\alpha} - 1), \infty)$ it 
decreases with $\alpha$. Following the arguments for Lemma~\ref{thrm:I},
in particular  using Lemma \ref{lemma:I}, it can be seen that
$\wt u_{\rm max}(\alpha, K)$ 
increases/decreases with $\alpha$ when $U_{\text{all}}(x)$ 
decreases/increases.

\subsection{Student's t-distributed equity return}
{\red This section is incomplete unless we can show results for $b>0$. Otherwise, we can do everything for $b=0$.} 
It is a common practice to use Student's t-distribution to model the
stationary distribution of equity returns. So it is of interest to
find out what implications this distribution has when it is combined
with the PDA preference. Formally we assume {\red instead of this function one can take a symmetric \ds\ with tails
$\P(X>x)=0.5 (\kappa/(x+\kappa))^{\alpha}$. If the symmetry causes another behavior than in the previous section this would be interesting.}
{\blue our tail-index is always $\alpha$, not $\nu$.}
\[
f(x; \alpha) = c(\alpha) \left(
  1 + {x^2 \over \alpha}
\right)^{-(\alpha + 1)/2}
\]
where $\alpha > 1$ and
\[
c(\alpha) = {
  \Gamma({\alpha + 1 \over 2})
  \over
  \Gamma(\alpha/2) \sqrt{\alpha \pi}
}
\]
In the same way as for \eqref{eq:ipf}, we can write $\wt u(F, \phi)$
as
\begin{eqnarray}
  && \wt u(F, \phi) \nonumber \\
  &=&
  (1 + b)
  \int_{0}^{\infty}
  \underbrace{
    \left\{
      u(C(x)) \left[
        1 - {b \over 1 + b}\1_{\{x \ge q\}}
        \right]
      + u(C(-x))
    \right\}
  }_{U_{\text{all}}}
  f(x, \alpha) dx
  - b u(\delta v) F_X(q)
  \label{eq:t1}
\end{eqnarray}
where $C(\cdot)$ is defined in \eqref{eq:xxie1}. As shown in lemma
\ref{lemma:III}, when $b = 0$ and $u(\cdot)$
takes the power-form of \eqref{eq:hjyr}, $U_{\text{all}}$ is monotone
depending on the values of $\xi$ and $(1 - \phi) e^r / \phi$. As given
in lemma \ref{lemma:II}, there is a point $x_0 > 0$ such that
${\pd f \over \pd \alpha}(x_0, \alpha) = 0$ and
$\forall x \in (0, x_0),
{\pd f \over  \pd \alpha}(x, \alpha) > 0$ and
$\forall x \in (x_0, \infty)$,
${\pd f \over \pd \alpha}(x, \alpha) < 0$. Thus it remains to verify
$\int_0^\infty |{\pd f \over \pd \alpha}(x, \alpha)| dx < \infty$ and
$\int_0^\infty |U_{\text{all}}(x){\pd f \over \pd \alpha}(x, \alpha)| dx < \infty$
if we are to apply lemma \ref{lemma:I}.

@@

\begin{figure}[htb!]
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_b_t_power.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{U_b_t_power.pdf}
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_b_t_power4.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{U_b_t_power4.pdf}
  \end{minipage}
  \caption{$\hat\phi$ (left) and ${\pd \tilde u_{\rm max} \over \pd
      \alpha}$ (right). {\em top:} $\xi = 1/2$. {\em bottom:} $\xi =
    4$.
  }
  \label{fig:htfg}
\end{figure}

% \subsubsection{log-utility function}
% We first consider the case where the utility function is simply
% $u(\cdot) = \log(\cdot)$. This corresponds to the limiting case of
% \eqref{eq:u} as $\gamma \to 0$.

% First notice that when $b = 0$, $\wt u(F, \phi)$ reduces to
% $\E u(C(X, \phi))$. Only the first integral of \eqref{eq:t1} remains.
% Its integrand becomes $\log[C(x, \phi) C(-x, \phi)]$.
% Now observe $\log(C(x, \phi)C(-x, \phi))$ is an increasing function of
% $x$:
% \begin{eqnarray*}
%   {\pd C(x, \phi) C(-x, \phi) \over \pd x}
%   &=&
%   \phi e^r (1 - \phi) (e^x - e^{-x}) > 0
% \end{eqnarray*}
% Thus when $b = 0$, by 1st case of remark \ref{remark:I} and lemma
% \ref{lemma:II}, {\red need to look at $\pd \wt u_{\rm max} \over \pd \alpha$?} 
% ${\pd \wt u(F, \phi)) \over \pd \alpha} < 0$ for all $\phi$. Hence all
% investors guided by this utility function would be seeking the
% smallest $\alpha$, i.e. the heaviest tail in the market. Here note that
% Student's t is a symmetric distribution; a heavier tail implies not
% only greater down-side risk but also greater up-side potential.

% In fact, even when $b > 0$, the same monotonicity property holds. This
% is revealed by numerically maximizing $\wt u(F, \phi)$ with
% respect to $\phi$ for a sequence of selected values of $\alpha$. The
% results are shown in figure~\ref{fig:phi_hat_U}.
% \begin{figure}[htb!]
%   \begin{minipage}{0.5\linewidth}
%     \includegraphics[width=\textwidth]{phi_hat_b_t_log.pdf}
%   \end{minipage}\hfill
%   \begin{minipage}{0.5\linewidth}
%     \includegraphics[width=\textwidth]{U_b_t_log.pdf}
%   \end{minipage}
%   \caption{$\hat\phi$ and $\tilde u_{\rm max}(\alpha)$
%     \label{fig:phi_hat_U}
%   }
% \end{figure}

\section{Conclusion}
\label{sec:4}
TODO: Summarize and conclude that all correlated series share the same
tail-index; their tail functions differ from each other via their
scale parameters.

\appendix
\section{A monotonicity lemma}
\setcounter{equation}{0}
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x, \theta)$ parameterized by 
  $\theta \in \Theta \subseteq \mathbb R$ has support
  $(a, b) \subseteq \mathbb R$,
  and in addition $F(x, \theta)$ has density
  function $f(x, \theta)$ that is differentiable with respect to
  $\theta$ for all $\theta \in \Theta$.
  Let $X \sim F$ and assume function $h(\cdot)$ is defined on $(a, b)$
  and is monotone throughout this interval.
  Moreover, we assume $h(x)$ and $f(x, \theta)$ satisfy
  \begin{equation}\label{eq:frt}
%    \E |h(X)| < \infty, \quad
    \int_a^b \left| {\pd f(x, \theta) \over \pd \theta} \right| dx
    < \infty \text { and }
    \int_a^b \left| h(x) {\pd f(x, \theta) \over \pd \theta} \right| dx
    < \infty
  \end{equation}
  Then the following holds true:
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\frac{\pd f}{\pd \theta}(x, \theta) > 0$ for $x \in (a, x_0)$ while
    $\frac{\pd f}{\pd \theta}(x, \theta) < 0$ for $x \in (x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\frac{\pd f}{\pd \theta}(x, \theta) < 0$ for $x \in (a, x_0)$  while
    $\frac{\pd f}{\pd \theta}(x, \theta) > 0$ for $x \in (x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\frac{\pd f}{\pd \theta}$
    satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\frac{\pd \E h(X)}{\pd \theta} < 0$. This immediately follows
    from applying 1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    ${\pd f \over \pd \theta}$ satisfies the same conditions of the
    2nd case of lemma \ref{lemma:I}, ${\pd \E h(X) \over \pd \theta} < 0$.
  \end{enumerate}
\end{remark}

>>>>

\subsection{A utility based argument for equal tail-indices}\label{sec:3}
In this section we give an argument based on economic theory that
suggests equality of  tail-indices for equity return series.
We follow an approach by Routledge and Zin
\cite{routledge2010generalized} who introduced the notion of
Generalized Disappointment Aversion (GDA). We consider the risky
payoff $C$ of an investor and assume that it has a continuous \ds\ on
$(0,\infty)$ with \df\ $F_C$. Let $u$ be a utility \fct\ assumed to be
increasing and concave on $(0,\infty)$.  Following Routledge and Zin
\cite{routledge2010generalized},
the utility of an agent with GDA preferences is given by
\beao% \label{eq:xxie0}
  \wt u&=& \E [u(C)] - b\, \int_{0}^{\delta v}
  \big[ u(\delta \,v) - u(x) \big] F_C(dx)\,,
  %&=&
  %\E u(C) - b \E\big[\big(u(\delta \,v) - u(C)\big)\1( C \le  \delta \,v)\big]\,,
\eeao
where $\delta $ and $v$ are positive constants, and $b\ge 0$.
  Here $v$ can be thought of as the {\em certainty payoff} equivalent to the
 risky payoff $C$; $\delta$ tunes the {\em threshold of 
   disappointment} in proportion to $v$; $b$ determines the extra
 weight given to the expected return of $C$ when $C$ is below the
 disappointment threshold $\delta v$.
 If $b=0$, preferences are the classical expected utility. If
 $\delta=1$ and $b>0$ preferences follow Gul's \cite{gul:1991} 
disappointment aversion which were generalized by Routledge and Zin
\cite{routledge2010generalized}.
\par
An agent guided by the utility function $u$ will seek to maximize the
\fct al $\wt u$.
Routledge and Zin assumed a power-law utility function 
\beam\label{eq:hjyr}
u(x)=-\frac{1}{\xi}\,x^{-\xi}\,,\quad \xi>0\,. 
\eeam

For the sake of argument, we assume that an investor initially has one
unit of wealth. He invests $1-\phi\in (0,1)$ units in a risk-free 
bond with interest rate $r>0$ and $\phi$ units in a risky asset with
return $X$ over one time unit, i.e.,
\beam\label{eq:xxie1}
  C(X) = (1 - \phi)\, \ex^{r} + \phi \,\ex^{X}\,.
\eeam
Then we have 
\beao
\wt u(F_X, \phi) &=& \E [u(C)] + b\, \E \big[u(C)\1(C \le  \delta v)\big] - b \,u(\delta\, v) F_X(q)\,,
\eeao
where $F_X$ is the \df\ of $X$  and
\beao
  q = %q(r, \phi) &:=& \log \left( {
      %\delta v - (1 - \phi) e^r
      %\over
      %\phi
    % \right) 
\log\Big(
    \ex^r + {\delta \,v - \ex^r \over \phi}
  \Big)\,.
\eeao
Note that $C \le \delta v$ \fif\ $X \le  q$. 
\par
Naturally, if an agent invests in
a risky asset instead of a riskless bond, he expects to obtain a
higher (on average) return from the risky asset than he is guaranteed from the
riskless bond. In our notation, this means $\delta \,v > \ex^r$ or
$q > r $. For given $b,\delta,v$, the \fct al $\wt u$  depends only on $\phi$ and $F_X$,
$\wt u=\wt u (F_X, \phi)$.
We assume that
\beao
\wt u_{\rm max}=\wt u_{\rm max}(F_X) = \max_{0 \le  \phi \leq 1} \wt u (F_X,\phi)
\eeao
exists and that the maximum is achieved at a unique $\hat\phi \in (0, 1)$.

@@

\begin{minipage}{0.5\linewidth}
  \includegraphics[width=\textwidth]{power_utilities.png}
\end{minipage}\hfill
\begin{minipage}{0.42\textwidth}
  The economitrical differences between the two utility functions
  are illustrated in the graph to the left.
  We see that
  $u(x)$ grows slower and saturates later for small $\xi$ than for
  large $\xi$. The latter case represents an agent who is more
  tolerant about low consumption and seeks wealth more
  aggressively. In other words, he is less risk-averse than one with a
  larger $\xi$. Such an agent will therefore invest more heavily in
  equity, as shown in Figure~\ref{fig:phi_hat_pareto}. Note that,
  while $\hat \phi$ changes nearly in the same in both graphs, the
  scales in the graphcs are very different.
\end{minipage}

\begin{figure}[htb!]
  \begin{minipage}{0.25\linewidth}
    \includegraphics[width=\textwidth]{preference_pareto5e-1_A.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.25\linewidth}
    \includegraphics[width=\textwidth]{preference_pareto4_A.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.25\linewidth}
    \includegraphics[width=\textwidth]{preference_pareto5e-1.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.25\linewidth}
    \includegraphics[width=\textwidth]{preference_pareto4.pdf}
  \end{minipage}
  \caption{
   {\em The 1st and 2nd} graphs show
   $\tilde u_{\rm max}(\alpha, K)$, as a \fct\ of $\alpha$ and $K$
   in the two-sided Pareto model \eqref{eq:pareto} with $K'=0.012$,
   $\beta = 1.4$.
   Clearly, $\tilde u_{\rm max}(\alpha, K)$ increases with $\alpha$
   and decreases with $K$ when $K'$ and $\beta$ are fixed.
   {\em The 3rd and 4th} graphs show
   $\tilde u_{\rm max}(\alpha, K)$ as a \fct\ of $\alpha$
   and $K$ with $\beta = \alpha$ and $K' = K$.
   We choose the utility \fct\ $u$ from \eqref{eq:hjyr} for $\xi = 1/2$
   and $\xi = 4$. $b = 0.01$ in all cases.
  }
  \label{fig:preference_pareto}
\end{figure}

If the parameter $b$ is very small the GDA preference is closely
approximated by the mean-utility preference, corresponding to $b = 0$. 
In this case, we show in the proof of Lemma \ref{lemma:III} that the function
$U_{\text{all}}(x)$ may increase or decrease depending on particular conditions
on the values of $\xi$ and $(1 - \phi) e^r / \phi$:
\begin{enumerate}
\item If $\max\{a, 1\} < \xi$, $U_{\text{all}}(\cdot)$ is
  monotone decreasing.
\item If $a < \xi < 1$ and $(a + y_-)/(a y_- + 1) <
  y_-^{(1-\xi)/(1+\xi)}$, $U_{\text{all}}(\cdot)$ is monotone
  decreasing.
\item If $\xi < a < 1$, $U_{\text{all}}(\cdot)$ is monotone
  increasing.
\item If $1 < \xi < a$ and $(a + y_+)/(a y_+ + 1) >
  y_+^{(1-\xi)/(1+\xi)}$, $U_{\text{all}}(\cdot)$ is monotone
  increasing.
\item In other case, $U_{\text{all}}(\cdot)$ is not monotone.
\end{enumerate}
where
\begin{eqnarray*}
a &=& {
  (1 - \phi) e^r
  \over
  \phi
} \\
y_\pm &=& {
  a^2 - \xi \pm \sqrt{(a^2 - 1) (a^2 - \xi^2)}
  \over
  a (\xi - 1)
}
\end{eqnarray*}
Moreover, it is also easily checked that, when
$x \in (0, K(e^{1/\alpha} - 1)]$,
the density function in the integral of \eqref{eq:ipf} increases
with $\alpha$; when $x \in (K(e^{1/\alpha} - 1), \infty)$ it 
decreases with $\alpha$. Following the arguments for Lemma~\ref{thrm:I},
and applying Lemma \ref{lemma:I}, it can be seen that
$\wt u_{\rm max}(\alpha, K)$ increases/decreases with $\alpha$ when
$U_{\text{all}}(x)$  decreases/increases.

\section{Conclusion}
\label{sec:4}
{\red Casper, we believe you are the most knowledgeable to conclude.}
\appendix
\section{A monotonicity lemma}
\setcounter{equation}{0}
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x, \theta)$ parameterized by 
  $\theta \in \Theta \subseteq \mathbb R$ has support
  $(a, b) \subseteq \mathbb R$,
  and in addition $F(x, \theta)$ has density
  function $f(x, \theta)$ that is differentiable with respect to
  $\theta$ for all $\theta \in \Theta$.
  Let $X \sim F$ and assume function $h(\cdot)$ is defined on $(a, b)$
  and is monotone throughout this interval.
  Moreover, we assume $h(x)$ and $f(x, \theta)$ satisfy
  \begin{equation}\label{eq:frt}
%    \E |h(X)| < \infty, \quad
    \int_a^b \left| {\pd f(x, \theta) \over \pd \theta} \right| dx
    < \infty \text { and }
    \int_a^b \left| h(x) {\pd f(x, \theta) \over \pd \theta} \right| dx
    < \infty
  \end{equation}
  Then the following holds true:
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\frac{\pd f}{\pd \theta}(x, \theta) > 0$ for $x \in (a, x_0)$ while
    $\frac{\pd f}{\pd \theta}(x, \theta) < 0$ for $x \in (x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\frac{\pd f}{\pd \theta}(x, \theta) < 0$ for $x \in (a, x_0)$  while
    $\frac{\pd f}{\pd \theta}(x, \theta) > 0$ for $x \in (x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\frac{\pd f}{\pd \theta}$
    satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\frac{\pd \E h(X)}{\pd \theta} < 0$. This immediately follows
    from applying 1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    ${\pd f \over \pd \theta}$ satisfies the same conditions of the
    2nd case of lemma \ref{lemma:I}, ${\pd \E h(X) \over \pd \theta} < 0$.
  \end{enumerate}
\end{remark}

\begin{proof}
  Firstly, by dominated convergence theorem, conditions \eqref{eq:frt}
  imply, for all $S \subseteq (a, b)$,
  \begin{eqnarray*}
    {\pd \over \pd \theta}\int_S f(x, \theta) dx
    &=&
    \int_S {\pd \over \pd \theta} f(x, \theta) dx \\
    {\pd \over \pd \theta}\int_S h(x) f(x, \theta) dx
    &=&
    \int_S h(x) {\pd \over \pd \theta} f(x, \theta) dx \\
  \end{eqnarray*}
  Thus we have
  \begin{eqnarray*}
    {\pd \E h(X) \over \pd \theta}
    &=&
    {\pd \over \pd \theta}
    \int_a^b h(x)
    f(x, \theta) dx \\
    &=& \int_a^b h(x)
    {\pd f \over \pd \theta}(x, \theta) dx \\
    &=& \underbrace{\int_a^{x_0}
      h(x) {\pd f \over \pd \theta}(x, \theta) dx}_{I_1}
    + \underbrace{\int_{x_0}^b
      h(x) {\pd f \over \pd \theta}(x,
      \theta) dx}_{I_2}
  \end{eqnarray*}
  $x_0$ being located in the interior of $(a, b)$ and
  $h(\cdot)$ being monotone imply $h(x_0) < \infty$.
  \begin{enumerate}
  \item When $h(x)$ is decreasing on $(a, b)$ and ${\pd f \over \pd
    \theta}(x, \theta) > 0$ on $(a, x_0)$
    \[
    I_1 > h(x_0) \int_a^{x_0}
    {\pd f \over \pd \theta}(x, \theta) dx
    \]
    Similarly, because ${\pd f \over \pd \theta}(x, \theta) < 0$ for
    $x \in (x_0, b)$ and $h(x)$ is decreasing, we have
    \begin{eqnarray*}
      I_2 &=& \int_{x_0}^b -h(x_0)
      \left|{\pd f \over \pd \theta}(x, \theta) \right| dx
      > -h(x_0)
      \int_{x_0}^b \left| 
        {\pd f \over \pd \theta}(x, \theta)
      \right| dx
    \end{eqnarray*}
    Finally we have
    \begin{eqnarray*}
      {\pd \E h(X) \over \pd \theta}
      > h(x_0) \int_a^b
      {\pd f \over \pd \theta}(x, \theta) dx
      = h(x_0) {\partial \over \partial \theta}
      \int_a^b f(x, \theta) dx
      = 0
    \end{eqnarray*}
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    ${\pd f \over \pd \theta}(x_0, \theta) < 0$ on $(a, x_0)$  while
    ${\pd f \over \pd \theta}(x_0, \theta) > 0$ on $(x_0, b)$, 
    by similar arguments, one can show
    \[
    {\pd \E h(X) \over \pd \theta}> 0
    \]
\end{enumerate}
\end{proof}

\section{When equity returns follow Student's t-distribution}
\setcounter{equation}{0}
It is a common practice to use Student's t-distribution to model the
stationary distribution of equity returns. So it is of interest to
find out what implications this distribution has when it is combined
with the PDA preference. Formally we assume
\[
f(x; \alpha) = c(\alpha) \left(
  1 + {x^2 \over \alpha}
\right)^{-(\alpha + 1)/2}
\]
where $\alpha > 1$ and
\[
c(\alpha) = {
  \Gamma({\alpha + 1 \over 2})
  \over
  \Gamma(\alpha/2) \sqrt{\alpha \pi}
}
\]
In the same way as for \eqref{eq:ipf}, we can write $\wt u(F, \phi)$
as
\begin{small}
  \begin{eqnarray}
    \wt u(F, \phi)
    &=&
    (1 + b)
    \int_{0}^{\infty}
    \underbrace{
      \left\{
      u(C(x)) \left[
        1 - {b \over 1 + b}\1_{\{x \ge q\}}
        \right]
      + u(C(-x))
      \right\}
    }_{U_{\text{all}}}
    f(x, \alpha) dx - b u(\delta v) F_X(q)
    \label{eq:t1}
  \end{eqnarray}
\end{small}
where $C(\cdot)$ is defined in \eqref{eq:xxie1}. As shown in lemma
\ref{lemma:III}, when $b = 0$ and $u(\cdot)$
takes the power-form of \eqref{eq:hjyr}, $U_{\text{all}}$ is monotone
depending on the values of $\xi$ and $(1 - \phi) e^r / \phi$. As given
in lemma \ref{lemma:II}, there is a point $x_0 > 0$ such that
${\pd f \over \pd \alpha}(x_0, \alpha) = 0$ and
$\forall x \in (0, x_0),
{\pd f \over  \pd \alpha}(x, \alpha) > 0$ and
$\forall x \in (x_0, \infty)$,
${\pd f \over \pd \alpha}(x, \alpha) < 0$. Thus it remains to verify
$\int_0^\infty |{\pd f \over \pd \alpha}(x, \alpha)| dx < \infty$ and
$\int_0^\infty |U_{\text{all}}(x){\pd f \over \pd \alpha}(x, \alpha)| dx < \infty$
if we are to apply lemma \ref{lemma:I}.

@@

\begin{figure}[htb!]
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_b_t_power.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{U_b_t_power.pdf}
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_b_t_power4.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{U_b_t_power4.pdf}
  \end{minipage}
  \caption{$\hat\phi$ (left) and ${\pd \tilde u_{\rm max} \over \pd
      \alpha}$ (right). {\em top:} $\xi = 1/2$. {\em bottom:} $\xi =
    4$.
  }
  \label{fig:htfg}
\end{figure}
\begin{lemma}
  \label{lemma:II}
  Let $f$ denotes the density function of the Student's
  t-distribution, i.e.
  \[
  f(x; \alpha) = c(\alpha) \left(
    1 + {x^2 \over \alpha}
  \right)^{-(\alpha + 1)/2}
  \]
  where $\alpha > 1$ and
  \[
  c(\alpha) = {
    \Gamma({\alpha + 1 \over 2})
    \over
    \Gamma(\alpha/2) \sqrt{\alpha \pi}
  }
  \]
  Then there exists $x_0 > 0$ such that ${\pd f \over
    \pd \alpha}(x_0, \alpha) = 0$ and $\forall x \in (0, x_0), {\pd f \over
    \pd \alpha}(x, \alpha) > 0$ and $\forall x \in (x_0, \infty), {\pd f
    \over \pd \alpha}(x, \alpha) < 0$.
\end{lemma}
\begin{proof}
  Straightforward computation gives
  \begin{eqnarray}
    {\pd f(x, \alpha) \over \pd \alpha} &=& {
      c(\alpha) x^2 (\alpha + 1) + (2 \alpha x^2 + 2 \alpha^2) c'(\alpha)
      -
      \alpha c(\alpha) (x^2 + \alpha) \log(1 + x^2/\alpha)
      \over
      2 \alpha (x^2 + \alpha) (1 + x^2 / \alpha)^{\alpha/2 + 1/2}
    } \nonumber \\
    &:=& {
      P(x^2, \alpha)
      \over
      2 \alpha (x^2 + \alpha) (1 + x^2 / \alpha)^{\alpha/2 + 1/2}
    }
    \label{eq:xxie4.1}
  \end{eqnarray}
